### 2014-07-11 Paper_v1.tex
New sections

\section*{Results}
We developed two proof of concept metabolic networks to investigate the features of our effective cell free modeling approach (Fig. \ref{fig-networks}).
In both examples, substrate $S$ was converted to the end-products $P_{1}$ and $P_{2}$ through a series of enzymatically catalyzed reactions, 
including a branch point at hypothetical metabolite $M_{2}$. 
Several of these reactions involved cofactor dependence ($AH$ or $A$), and various allosteric regulation mechanisms. 
Network A included feedback inhibition of the initial pathway enzyme ($E_{1}$) by pathway end products $P_{1}$ and $P_{2}$ (Fig. \ref{fig-networks}A).
On the other hand, network B involved feedback inhibition of $E_{1}$ by $P_{2}$ and $E_{6}$ by $P_{1}$ (Fig. \ref{fig-networks}B). 
In both networks, branch point enzymes $E_{3}$ and $E_{6}$ were subject to feed-forward activation by cofactor $AH$.
Lastly, enzyme activity was assumed to decay according to a first-order rate law in both cases. 
Allosteric regulation of enzyme activity was represented using a novel rule-based strategy, similar in spirit to the 
Constrained Fuzzy Logic (cFL) approach of Lauffenberger and coworkers \citep{Morris:2011aa}. 
In this formulation, Hill-like transfer functions were used to calculate the influence of metabolite abundance upon target enzyme activity. 
When an enzyme was potentially sensitive to more than one regulatory influence, logical rules were used to select which transfer function regulated enzyme 
activity at any given time (Fig. \ref{fig-control-schematic}).      
Thus, our test networks involved important features such as cofactor recycling, enzyme activity and metabolite dynamics, 
as well as multiple overlapping allosteric regulatory mechanisms.  
As such, developing our effective modeling approach using these simple problems gave us valuable insight into the development of larger network models, 
without the complication of network size.

@@

The estimation of kinetic parameters was sensitive to the choice of regulatory structure (Fig. \ref{fig-parameter-fit}).
A critical challenge for any dynamic model is the estimation of kinetic parameters. 
For metabolic processes, there is also the added challenge of identifying the regulation and control structures that manage metabolism.  
Of course, these issues are not independent; any description of enzyme activity regulation will be a function of system state, which
in turn depends upon the kinetic parameters. For cell free systems, regulated gene expression has been removed, however, enzyme activity regulation is still operational. 
We explored this linkage by estimating model parameters from synthetic data using both network
structures. We generated noise-corrupted synthetic measurements of the substrate $S$, intermediate $M_{5}$ and end-product $P_1$ approximately every 20 min using
network A. We then generated an ensemble of model parameter estimates by minimizing the difference between model simulations and the synthetic data using particle swarm
optimization, starting from random initial guesses. 
PSO identified an ensemble of parameters that bracketed the mean of the synthetic measurements in less than 1000 iterations when the control structure was correct (Fig. \ref{fig-parameter-fit}A and B).
However, when there was model mismatch (network B fit against network A data), PSO was not able to identify an ensemble, all else being the same (Fig. \ref{fig-parameter-fit}C and D).

>>>>

\section*{Results}

\subsection*{Formulation and properties of cell free effective models.}
We developed two proof of concept metabolic networks to investigate the features of our effective cell free modeling approach (Fig. \ref{fig-networks}).
In both examples, substrate $S$ was converted to the end-products $P_{1}$ and $P_{2}$ through a series of enzymatically catalyzed reactions, 
including a branch point at hypothetical metabolite $M_{2}$. 
Several of these reactions involved cofactor dependence ($AH$ or $A$), and various allosteric regulation mechanisms. 
Network A included feedback inhibition of the initial pathway enzyme ($E_{1}$) by pathway end products $P_{1}$ and $P_{2}$ (Fig. \ref{fig-networks}A).
On the other hand, network B involved feedback inhibition of $E_{1}$ by $P_{2}$ and $E_{6}$ by $P_{1}$ (Fig. \ref{fig-networks}B). 
In both networks, branch point enzymes $E_{3}$ and $E_{6}$ were subject to feed-forward activation by cofactor $AH$.
Lastly, enzyme activity was assumed to decay according to a first-order rate law in both cases. 
Allosteric regulation of enzyme activity was represented using a novel rule-based strategy, similar in spirit to the 
Constrained Fuzzy Logic (cFL) approach of Lauffenberger and coworkers \citep{Morris:2011aa}. 
In this formulation, Hill-like transfer functions were used to calculate the influence of metabolite abundance upon target enzyme activity. 
When an enzyme was potentially sensitive to more than one regulatory influence, logical rules were used to select which transfer function regulated enzyme 
activity at any given time (Fig. \ref{fig-control-schematic}).      
Thus, our test networks involved important features such as cofactor recycling, enzyme activity and metabolite dynamics, 
as well as multiple overlapping allosteric regulatory mechanisms.  
As such, developing our effective modeling approach using these simple problems gave us valuable insight into the development of larger network models, 
without the complication of network size.

@@

\subsection*{Estimating parameters and effective allosteric regulatory structures.}
A critical challenge for any dynamic model is the estimation of kinetic parameters. 
For metabolic processes, there is also the added challenge of identifying the regulation and control structures that manage metabolism.  
Of course, these issues are not independent; any description of enzyme activity regulation will be a function of system state, which
in turn depends upon the kinetic parameters. For cell free systems, regulated gene expression has been removed, however, enzyme activity regulation is still operational. 
We explored this linkage by estimating model parameters from synthetic data using both network
structures. We generated noise-corrupted synthetic measurements of the substrate $S$, intermediate $M_{5}$ and end-product $P_1$ approximately every 20 min using
network A. We then generated an ensemble of model parameter estimates by minimizing the difference between model simulations and the synthetic data using particle swarm
optimization, starting from random initial guesses. 
The estimation of kinetic parameters was sensitive to the choice of regulatory structure (Fig. \ref{fig-parameter-fit}).
PSO identified an ensemble of parameters that bracketed the mean of the synthetic measurements in less than 1000 iterations when the control structure was correct (Fig. \ref{fig-parameter-fit}A and B).
However, when there was network mismatch (network B fit against network A synthetic data), PSO unable to identify an ensemble, all else being the same (Fig. \ref{fig-parameter-fit}C and D).
Interestingly, the particle swarm generated a \textit{sloppy} parameter ensemble, in the absence of network mismatch (Fig. ZZZ).

We modified our particle swarm identification strategy to simultaneously search over control structures and kinetic parameters (Fig. ZZZ). 
We constructed five putative network models, each with the same enzymatic connectivity but different allosteric structures (Fig. ZZZ). 
We then initialized a population of particles, each with one of the five putative regulatory programs, and randomized kinetic parameters.
We biased the distribution of the particle population according to \textit{a~prior} belief of the correct regulatory program.
To this end, we considered three different priors, a uniform distribution where each of the regulatory structures represented 20\% of the population, and
two mixed distributions that were positively and negatively biased towards the correct structure (Table ZZ).
